---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timewarp

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/DavisVaughan/timewarp.svg?branch=master)](https://travis-ci.org/DavisVaughan/timewarp)
[![Codecov test coverage](https://codecov.io/gh/DavisVaughan/timewarp/branch/master/graph/badge.svg)](https://codecov.io/gh/DavisVaughan/timewarp?branch=master)
[![R build status](https://github.com/DavisVaughan/timewarp/workflows/R-CMD-check/badge.svg)](https://github.com/DavisVaughan/timewarp)
<!-- badges: end -->

The goal of timewarp is to provide tooling to group date times by period, and manipulate the groups.

```{r}
library(timewarp)
```

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DavisVaughan/timewarp")
```

## Example

One of the core functions in timewarp is `warp_group()`, which allows you to provide a date time vector and specify a period to group it by. For example, we can group this vector by month.

```{r}
x <- as.Date("1970-01-01") + -2:2
x

warp_group(x, by = "month")
```

The groups that `warp_group()` returns have values that correspond to the distance from `x` to the `origin`, in units defined by the `by` period and the width defined by `every`. The `origin` defaults to the unix epoch of `1970-01-01 00:00:00`, but you can change that. In this case the groups are saying that, for example, `"1970-01-02"` is in the same month as the origin, and `"1969-12-31"` is 1 month group away.

You can also group by days. Rather than grouping by 1 day, let's group every 2 days together, starting from the default `origin`.

```{r}
# Groups 1970-01-01 and 1970-01-02 together
warp_group(x, by = "day", every = 2)
```

You will often want to set your own `origin` date. Let's shift it forward 1 to `1970-01-02`.

```{r}
origin <- as.Date("1970-01-02")
origin

# Groups 1970-01-02 and 1970-01-03 together
warp_group(x, by = "day", every = 2, origin = origin)
```

## Inspiration

The algorithm for `warp_group()` was inspired by `xts::endpoints()`.
